Local PCA results

### 2017-04-22 templated/summarize_run.Rmd
small changes

sample.ids <- vcf_samples(bcf.files[1])
if (!is.null(opt$sample_info)) {
    samp.file <- opt$sample_info
    samps <- read.table(samp.file,sep="\t",header=TRUE)
    samps <- droplevels( samps[match(sample.ids,samps$ID),] )
    samps$population <- factor(samps$population)
} else {
    samps <- data.frame( 
            ID=sample.ids,
            population=factor(rep("pop",length(sample.ids))) )
}

>>>>

sample.ids <- vcf_samples(bcf.files[1])
if (!is.null(opt$sample_info)) {
    samp.file <- opt$sample_info
    samps <- read.table(samp.file,sep="\t",header=TRUE)
    names(samps) <- tolower(names(samps))
    samps <- droplevels( samps[match(sample.ids,samps$id),] )
    samps$population <- factor(samps$population)
} else {
    samps <- data.frame( 
            ID=sample.ids,
            population=factor(rep("pop",length(sample.ids))) )
}
